A Linear Solution of the Linearity Challenge

### 2025-12-24 paper/Congruence.lagda.tex
excusatio non petita accusatio manifesta

>>>>

We concede that the definition of these pre-congruence rules (including those
not discussed here) can be difficult to decipher. In part, this is due to the
fact that splitting proofs are manifest and no longer hidden within separating
conjunctions as we have done in \Cref{sec:process-agda} because we need them to
enforce the side conditions of the rules in \Cref{tab:semantics}. Also, using an
intrinsically-typed representation of processes, pre-congruence and reduction
rules incorporate the proof that they preserve typing.
